Lyman-$\alpha$ photons through rotating outflows

### 2018-03-31 paper/paper.tex
edit

\subsubsection{\lya continuum escape or rotation?}

Another application of this new model to the current interpretation of \lya
spectra, is that the central ($V=0$) emission of the spectra seen in the
\lya line, is a consequence of the viewing angle of the galaxy and can be
controlled by it. Several authors have suggested that this central emission
is caused by radiation that escapes the galaxy without scattering. So we
present an alternative that solves this issue. In addition, the effect of
outflows velocities \vrot in current models can modify the asymmetry of peaks
present in the \lya line. However the intensity of the valley and the width
of the line were not easily reproduced. In this work we provide a tool to
provide these effects with values of \vout and \vrot that do not exceed the
typical LAEs' values found in the literature.

>>>>

\subsubsection{\lya continuum escaping or rotation?}

Another application of this new model to the current interpretation of \lya
spectra, is that the central ($V=0$) emission of the spectra seen in the
\lya line, is a consequence of the viewing angle of the galaxy and can be
controlled by it. 
Several authors have suggested that this central emission is caused by
radiation that escapes the galaxy without scattering. 
Rotation is an alternative that solves this issue.

We note that the relative intensity of the two peaks in the outflowing
spectra is not modified by rotation, that asymmetry is solely
controled by the outflow velocity.
This means that results that have already derive a typical outflowing
velocity as to match the observational constraints do not have to be
completely revised. 
Only an additional exploration of rotational velocities and viewing
angles need to be explored.
